Proportional multi-state multiple-cohort life table model

### 2018-04-20 MSLT/MSLTdoc.Rmd
Order input life dataset

#input_life_table$pop_five_year <- ifelse(
#  input_life_table$sex_age_cat == GBD_population_GL$pop_five_year, #GBD_population_GL$pop_five_year, NA)

>>>>

##Cross check population numbers
sum(input_life_table$pop_five_year, na.rm = TRUE)
#Sort data by sex and age to use in life table function. 
input_life_table<-input_life_table[order(input_life_table$sex, input_life_table$age),]
